Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete final draft of paper

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment.

@@

On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general.

>>>>

Sentiment analysis is a technique of employing Machine Learning algorithms in order to infer a sentiment 
score from textual information. These algorithms need to be trained on very large data sets in order to 
produce valuable results. Moreover, we would have also needed an already annotated data set, which means 
a number of strings where we compute the score by hand given a mathematical formula we define. Even though 
there are open source libraries that can help creating and employing the algorithms, such as TensorFlow, 
we would still have needed tickets where we defined what do we mean by positive/negative tickets, as well as
manually computing the scores for a large range of them. Therefore, we ended using a third party API - Google 
Cloud Platform Natural Language Processing, considered the best such service at the moment. This API returns 
a score between -1 (most negative) and +1 (most positive) for any text encoded in the HTTP request.

@@

On the other side of the spectrum, having a more positive score leads to higher quality in tickets. Calefato et. al 
\cite{calefato2015mining} conducted a study where they show that a positive sentiment has the biggest impact on 
the quality of an answer on Stack Overflow, one of the most popular websites related to programming in general. This 
implies that when developers and triagers treat their reporters respectfully and offer support whenever possible, 
the users will feel more welcomed and willing to help report other bugs in the future as well. We also have scores of 
over 0.9, meaning that the actors participating in the discussion (or the reported summary/description) might compliment 
each other for doing a great job.

We strongly believe that having a positive sentiment score for tickets is valuable for absolutely everyone: the company
behind the projects sees increased overall performance and productivity, developers feel better working in the team or
on that specific tool and reporters will be more willing to contribute in the future with other tickets.

A solution for pushing towards this ideal scenario would be expensive for the company, but the most efficient - have a 
sentiment analysis tool running in the background as the user is typing in any text box. If they reach a certain low 
treshold and it is believed that they are becoming rude or unpolite, there could be a warning/pop-up on the screen advising 
them to not do that as it wouldn't help any party, but rather try to be polite, engaging and friendly. One other solution
is a much more cost-effective one, but less efficient - the issue tracking system administrators could include a section 
in the code of conduct for the project stating that promoting a positive environment will help everyone. This way, people 
revolving around the project might be more inclined to be friendly.
